Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-23 paper/paper.tex
Add new image scales and fix issues
Finish whole paper completely

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{images/flow.pdf}
\end{center}
\caption{\label{fig-eg}Application flow of the Go tool.}
\end{figure*}

@@

\vskip30pt

@@

\begin{figure}[ht]
  \begin{center}
  \includegraphics[scale=0.25]{images/attachments.png}
  \end{center}
  \caption{\label{attachments}Attachments analysis.}
\end{figure}

@@

\vskip18pt

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.25]{images/steps_to_reproduce.png}
  \end{center}
  \caption{\label{steps}Steps to reproduce analysis.}
\end{figure}

@@

\vskip12pt

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.25]{images/stack_traces.png}
  \end{center}
  \caption{\label{stack_traces}Stack traces analysis.}
\end{figure}

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.25]{images/comment_complexity.png}
  \end{center}
  \caption{\label{comments}Comments complexity analysis.}
\end{figure}

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.25]{images/fields_complexity.png}
  \end{center}
  \caption{\label{fields}Summary and Description Complexity Analysis.}
\end{figure}

@@

\vskip10pt

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.25]{images/grammar_correctness.png}
  \end{center}
  \caption{\label{grammar}Grammar correctness score analysis.}
\end{figure}

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.25]{images/sentiment_analysis.png}
  \end{center}
  \caption{\label{sentiment}Sentiment score analysis.}
\end{figure}

>>>>

In this section, several state-of-the art research studies revolving around software tickets and their surrounding 
environment were presented. The findings and techniques summarised proved useful for our own research, 
helping us build the data set as we will elaborate in the following section.

\begin{figure*}
\begin{center}
\includegraphics[scale=0.80]{images/flow.pdf}
\end{center}
\caption{\label{fig-eg}Application flow of the Go tool.}
\end{figure*}

@@

@@

\begin{figure}[ht]
  \begin{center}
  \includegraphics[scale=0.18]{images/attachments.png}
  \end{center}
  \caption{\label{attachments}Attachments analysis.}
\end{figure}

@@

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.18]{images/steps_to_reproduce.png}
  \end{center}
  \caption{\label{steps}Steps to reproduce analysis.}
\end{figure}

@@

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.18]{images/stack_traces.png}
  \end{center}
  \caption{\label{stack_traces}Stack traces analysis.}
\end{figure}

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.18]{images/comment_complexity.png}
  \end{center}
  \caption{\label{comments}Comments complexity analysis.}
\end{figure}

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.18]{images/fields_complexity.png}
  \end{center}
  \caption{\label{fields}Summary and Description Complexity Analysis.}
\end{figure}

@@

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.18]{images/grammar_correctness.png}
  \end{center}
  \caption{\label{grammar}Grammar correctness score analysis.}
\end{figure}

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.18]{images/sentiment_analysis.png}
  \end{center}
  \caption{\label{sentiment}Sentiment score analysis.}
\end{figure}
